---
title: "Assignment 2"
format: pdf
editor: visual
---

## Task 1

```{r}
rm(list=ls())
library(tidyverse)
library(rvest)#for scrapping
library(janitor)
library(lubridate)
#Loading all the packages needed.
```

```{r}
url <- "https://www.motor.no/aktuelt/motors-store-vintertest-av-rekkevidde-pa-elbiler/217132"

url %>% read_html() %>% 
  html_element("table") %>%  
  html_table()
```
```{r}
 df1 <- url %>%
   read_html() %>% 
   html_nodes("table") %>%  
   html_table() %>% .[[1]]
```


```{r}
names(df1) <- c("Modell (temp 0-10)", "WLTP-tall", "STOPP", "Avvik")
#Giving columns a title

df1 <- df1[-1,]
#Removing first row.
```


```{r}
#Duplicating columns
df1 <- separate(df1, col=`WLTP-tall`, into=c('WLTP-tall', 'NaN'), sep=' ')
df1 <- separate(df1, col=`STOPP`, into=c('STOPP', 'Remove'), sep=' ')
```

```{r}
df1$`WLTP-tall` <- as.numeric(df1$`WLTP-tall`)
df1$STOPP <- as.numeric(df1$STOPP)

df1 <- df1[-19,]
df1 <- df1[-25,]
```


```{r}
#plot
df1 %>%
  ggplot(aes(x= `WLTP-tall` , y = STOPP)) +
  geom_point() +
  geom_abline(intercept = 0, slope = 1, size = 1, col = 'red') +
  xlab('WLTP') +
  ylab('STOP') +
  ggtitle('WLTP vs. range in cold weather') +
  theme_minimal()
```
# The figure reveals that none of the cars meet their advertised range under the temperature conditions of 0 to -10 Celsius. Ideally, if the cars lived up to their advertised range, their data points would fall on the 45-degree line, while data points above the line would indicate that the cars exceeded their expected range.

## Task 2

```{r}
df2 <- lm(`STOPP` ~ `WLTP-tall`, data = df1)
```

# The regression line has a y-intercept of -26.645 and a positive slope of 0.8671, indicating an increase in the y-axis values with increasing x-axis values.

```{r}
#plot
df2 %>%
  ggplot(aes(x = `WLTP-tall`, y = STOPP)) + 
  geom_point()+
  geom_abline(intercept = 0, slope = 1, size = 0.5, col = 'red') +
  stat_smooth(method = "lm", col = "green") +
  xlab('WLTP') +
  ylab('STOP') +
  ggtitle('WLTP vs. range in cold weather') +
  theme_minimal()
```